### 2018-01-18 Chapters/Introduction.tex
Update on Overleaf.

The question, however, of whether Bitcoin (or related works) can scale to billions of people is far from settled.

@@

Iota is another cryptocurrency, but, instead of using a blockchain, it proposes the use a ``tangle architecture'', which is a different way to store the currency ledger across thousands of computers. Although it has not been confirmed in practice yet, its architecture seems to be significantly more scalable than Bitcoin's blockchain. As we will see, the problem here is exactly the opposite of Bitcoin's. It needs a minimum of transactions per seconds in order to work properly.

@@

A second topic that may have an outsized influence ion business and that we will be taking a closer look is a model of artificial intelligence.

\subsection{Artificial intelligence}
% Technology > Computer Science > Artificial Intelligence > Pattern Recognition > SDM.

@@

\section{Innovation adoption}

The third paper lies at the intersection of Marketing, Diffusion of Technological Innovation, and modeling. The classic Bass model of diffusion of innovation is extended, in order to account for users who, after adopting the innovation for a while, decide to reject it later on (possibly bringing down the number of active users---which is impossible in Bass' original model). Four alternative mathematical models are presented and discussed with the Facebook users dataset. %This is the work that has received most energy so far, and is the most mature of the papers presented herein.  I believe it is almost ready for submission for publication.

%A fourth paper is still highly immature.  It concerns monetary inflation, and the demonstrations that an approach through fixed effects cannot correct for the real cumulative inflation rates---and may be disastrous when referring to regions undergoing high inflation.  Though part of the mathematical analysis is mature, the work itself is lacking the necessary references to show its relevance:  I still need to review the literature and point out the rather large body of it that is committing a serious error. Because I have not decided whether this work should be part of the thesis, it will be presented in appendix 1.

It is my hope that readers of this proposal will accept the format of self-contained studies and will agree that---if the topics discussed herein are handled with the proper effort and care---the proposed body of work should be deemed worthy of the originality and the scientific significance implicit to the work of a Doctoral Thesis.

>>>>

The question of whether Bitcoin (or related works) can scale to billions of people is, however, far from settled.

@@

\emph{Iota} is a second cryptocurrency, which, instead of using a blockchain, proposes the use of a ``tangle' architecture': a different way to register the currency ledger across thousands of computers. Although it has not been confirmed in practice yet, its architecture seems to be significantly more scalable than Bitcoin's blockchain. As we will see, the problem here is exactly the opposite of Bitcoin's. Iota needs a minimum of transactions per seconds in order to work properly.

@@

A second topic that may have an outsized influence on business and that we will be taking a closer look is a model of artificial intelligence.

\section{Artificial intelligence}
% Technology > Computer Science > Artificial Intelligence > Pattern Recognition > SDM.

@@

\section{Diffusion of innovation}

In 2014, a group of Princeton's researchers predicted that Facebook's users would abandon the platform by 2017 \citep{cannarella2014epidemiological}. The forecast was done applying a disease spreading model which has correctly predicted the abandonment of ``MySpace''. Facebook replied applying exactly the same methodology as Princeton's researchers. In their own words: ``Using the same robust methodology featured in the paper, we attempted to find out more about this `Princeton University' -- and you won't believe what we found!''. Then, they conclude: ``This trend suggests that Princeton will have only half its current enrollment by 2018, and by 2021 it will have no students at all, agreeing with the previous graph of scholarly scholarliness. Based on our robust scientific analysis, future generations will only be able to imagine this now-rubble institution that once walked this earth''.

Whilst this brouhaha reminds one of the dangers of extrapolation, our third paper will revisit the prospects of our esteemed colleagues in Facebook. Lying at the intersection of Marketing, Diffusion of Technological Innovation, and modeling, the Bass model of diffusion of innovation will be extended, in order to account for users who, after adopting the innovation for a while, decide to reject it later on (possibly bringing down the number of active users---which is impossible in Bass' original model). Four alternative mathematical models are presented and discussed with the Facebook's users dataset.

\section{The fine print...}

Before embarking on the technical topics, small qualifications must be asked from my readers. First, as stated above, though these problems have immense and urgent importance to the fields of study in business, the language in which we will approach them and discuss them most naturally will be that of mathematics and computer science.  There will not be surveys, interviews, questionnaires, or such methods typically used in the social sciences: This is basically a work of modeling.

A second and final qualification: It is my hope that readers of this thesis will accept the format of self-contained studies and will agree that---if the topics discussed herein are handled with the proper effort and care---this body of work should be deemed worthy of the originality and the scientific significance implicit to the work of a Doctoral Thesis. Please bear with me as we venture into the world of computational management science.
